---
title: "Sample Mean Of Horspower & Miles/Gallon on Mtcars Dataset"
author: "Jeevan-1740256"
date: "13 December 2018"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\section{Aim}
mtcars data frame involves data on a 32 automobiles. Randomly select 30% of these automobiles and hence
i) calculate its average Miles/gallon and horsepower.
ii) Do this three times and note that they are unlikely to be the same automobiles.
iii) Display the identical result 3 times.
```{r}
data<-sample(1:nrow(mtcars),10)
data
newcars<-mtcars[data,]
newcars
mean(mtcars$hp)
mean(mtcars$mpg)
index<-sample(1:nrow(mtcars),10)
index
oldcars<-mtcars[index,]
oldcars
mean(mtcars$hp)
mean(mtcars$mpg)
flag<-sample(1:nrow(mtcars),10)
flag
medcars<-mtcars[flag,]
medcars
mean(mtcars$hp)
mean(mtcars$mpg)
```
\section{Result}
The Average Miles/gallon on the mtcars dataset is: 20.09062
The Average horspower on the mtcars dataset is: 146.6875
The Automobiles are different all the 3 times we excecute the code although the mean remains identical all 3 times. 