---
title: "Stratification in R"
author: "Jeevan"
date: "21 February 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
Stra_Data <- read_excel("C:/Users/Jeevan/Desktop/Christ University/Statistics/Stra_Data.xlsx")
View(Stra_Data)
library(dplyr)
male <- Stra_Data %>% select(Age,Sex,`Pain score at first intervention`,`Time from End of surgery (mins)`) %>% filter(Sex=='M')
female <- Stra_Data %>% select(Age,Sex,`Pain score at first intervention`,`Time from End of surgery (mins)`) %>% filter(Sex=='F')
strata1 <- Stra_Data %>% select(Age,Sex,`Pain score at first intervention`,`Time from End of surgery (mins)`) %>% filter(Age>=16 & Age<=25)
strata1
strata1 = filter(Stra_Data,Age>=16, Age<=30)
strata2 = filter(Stra_Data,Age>=31, Age<=40)
strata3 = filter(Stra_Data,Age>=41, Age<=60)
S1_size = round(nrow(strata1)/(nrow(Stra_Data))*60)
S2_size = round(nrow(strata2)/(nrow(Stra_Data))*60)
S3_size = round(nrow(strata3)/(nrow(Stra_Data))*60)
stmp1 = sample_n(strata1, S1_size)
stmp2 = sample_n(strata2, S2_size)
stmp3 = sample_n(strata3, S3_size)
```
The Stra_Data dataset has been imported into RStudio & the data has been split into male & female. 
The 1st stratum was created from the dataset which includes both male & female of the age group 16 to 25 years. 
```{r}
strata2 <- Stra_Data %>% select(Age,Sex,`Pain score at first intervention`,`Time from End of surgery (mins)`) %>% filter(Age>=26 & Age<=40)
strata2
```
The 2nd stratum was created from the dataset which includes both male & female of the age group 26 to 40 years. 
```{r}
strata3 <- Stra_Data %>% select(Age,Sex,`Pain score at first intervention`,`Time from End of surgery (mins)`) %>% filter(Age>=41 & Age<=60)
strata3
```
The 3rd stratum was created from the dataset which includes both male & female of the age group 41 to 60 years.

CONCLUSION
The dataset was divided into 3 different stratums; Stratum1(16 to 25), Stratum2(26 to 40), Stratum3(41 to 60). 
The stratums were grouped based on the age of the population. 
(i)Stratum1 consists of 52 datapoints i.e there are 52 people between the ages 16 & 25.
(ii)Stratum1 consists of 71 datapoints i.e there are 71 people between the ages 26 & 40.
(iii)Stratum1 consists of 27 datapoints i.e there are 27 people between the ages 41 & 60.