---
title: "Case_Study_1740256"
author: "Jeevan-1740256"
date: "24 January 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\section{Aim}
Analyse the churn in Telecom's dataset
```{r}
setwd("C:/Users/Jeevan/Desktop/Christ University/R Studio")   #setting the directory
datas = read.csv('bigml_59c28831336c6604c800002a.csv')    #importing the dataset
head(datas,5)   #1st 5 rows of the dataset
View(datas)   #viewing the whole dataset
summary(datas)   
names(datas)  #knowing the names of the columns in the sheet
mean.totaldaycalls = mean(datas$total.day.calls,na.rm = TRUE)      #getting the mean of total day calls
mean.totaldaycalls 
plot(datas$total.day.calls,datas$total.eve.calls,main = "Total Day Calls vs Total Evening Calls",xlab = "Total Day calls",ylab = "Total Evening Calls",pch=20,data = datas)   #plotting total day calls with total evening calls
abline(h=mean.totaldaycalls)  #adding the mean to the graph
model1=lm(total.day.calls~total.eve.calls,data=datas)   #getting a linear model
abline(model1,col="red")   #Fitting the linear model to the graph
plot(model1)  
plot(datas$total.eve.calls,datas$total.night.calls,main = "Total Evening Calls vs Total Night",xlab = "Total Evening calls",ylab = "Total Night",pch=20,col='red')
d=density(datas$total.day.calls)  #Kernel density plot
d
plot(d,main="Total Day Calls")
polygon(d,col="red",border="black")   
boxplot(datas$total.intl.charge,main = "Total International Charge",col="blue",border="brown",horizontal = TRUE,notch = TRUE)
datas$churn = factor(datas$churn,   #converting textual values to numerical values
                    levels = c('TRUE','FALSE'),
                    labels = c(1,0))
datas$voice.mail.plan = factor(datas$voice.mail.plan,
                              levels = c('yes','no'),
                              labels = c(1,0))
datas$international.plan = factor(datas$international.plan,
                                 levels = c('yes','no'),
                                 labels = c(1,0))
datas$total.day.calls = ifelse(is.na(datas$total.day.calls),
                        ave(datas$total.day.calls,FUN = function(x) mean(x,na.rm = TRUE)),
                        datas$total.day.calls)
datas$total.day.minutes = ifelse(is.na(datas$total.day.minutes),
                        ave(datas$total.day.minutes,FUN = function(x) mean(x,na.rm = TRUE)),
                        datas$total.day.minutes)
```

\section{Result}
In this case study, the excel sheet of churning the Telecom's dataset has been imported into RStudio. 
To have a rough overview of how the data is, the first 5 rows of the sheet has been coded. 
In the summary of the sheet - we can see minimum value, maximum value, 1st Quartile & 3rd Quartile deviation. The mean and the median for each column are also shown in the summary. 
The code with the names of the sheet tells us the different columns that are ther. 
We are finding the mean of total day calls to replace all the values that are not applicable.
We are then plotting the graph between Total Day calls & Total evening to see whether they are related.
Using the concept of linear regression, we are fitting a linear model to the graph of total day calls. 
A kernel density plot is shown of the total day calls which tells us that the graph is normally distributed. 
To replace the textual data - to make TRUE = 1 & FALSE = 0, we are using the factors function and labelling it with 1 & 0. This is the case for the churn column, voice mail plan and international plan. 
The total day calls and total day minutes might have nil values and we are replacing that with the mean of the corresponding column. 